Realistically Interesting Domains for Probabilistic Planners

### 2014-04-08 FinalPaper/paper.tex
rewritten gourmand

\subsection{\textsc{Gourmand}}
\textsc{Gourmand}, an online adaptation of the \textsc{Glutton} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}

>>>>

\subsection{\textsc{GOURMAND}}
The \textsc{GOURMAND} is an online adaptation of the \textsc{GLUTTON} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ and is dynamically chosen. At every iteration over the distance to the horizon $H$, it divides the total remaining time $\overline{T}$ equally amongst the remaining iterations and virtually allocates time: $T_t = \frac{\overline{T}}{H - t}$. During the first epoch, or iteration it estimates how long solving a state takes for different lookahead values. Using this estimate and a virtual time allocation \textsc{GOURMAND} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch still guaranteeing that it can solve both epochs. If so, it solves the current epoch for $\widehat{L}_t$ and otherwise $L_t$. This way \textsc{GOURMAND} never has to resort to default policies and converges relatively fast to a good policy in an online fashion. The \textsc{GOURMAND} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand}.
